---
title: "Transmission Risk"
author: "NB"
date: "2022-10-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(tidyverse)
library(tidybayes)

source("../utils/plotting.R")
```

## Data

```{r}
study_classes <- c("Study (A)", "Study (B)", "Study")

# environmental data
palas <- read_csv("../data-clean/left-palas-redcap.csv") %>%
  mutate(weekday = factor(weekday, levels = paste0(c("Mon", "Tues", "Wednes", "Thurs", "Fri"), "day")),
         intervention = factor(intervention, levels = c("None", "Mask mandate", "Air filter")))

palas_daily <- palas %>%
  filter(class %in% study_classes) %>%
  group_by(school, class, date, week, weekday, intervention, maskmandate, airfilter) %>%
  summarize(across(c(f, n_room, n_class), ~ median(.x, na.rm = T))) %>% 
  ungroup() %>%
  group_by(class) %>%
  arrange(date) %>%
  mutate(day = 1:n()) %>%
  ungroup()

palas_int <- palas %>%
  group_by(school, class, intervention) %>%
  summarise(median_f = median(f),
            sd_f = sd(f)) %>%
  ungroup()

# covid data  
redcap <- read_csv("../data-clean/redcap.csv") %>%
  filter(!no_school,
         class %in% study_classes) %>%
  group_by(school, class) %>%
  arrange(date) %>%
  mutate(day = 1:n()) %>%
  ungroup() 

redcap_sim <- meta_dat <- data.frame(folders = list.files("../fitted-models/multiverse", full.names = T),
                                     dataset = as.numeric(list.files("../fitted-models/multiverse"))) %>%
  mutate(sample_file = sapply(folders, list.files, pattern = "sample", full.names = T)) %>%
  mutate(observed_data = lapply(sample_file, readRDS)) %>%
  unnest() %>%
  select(sample_file, dataset, class, day, new_cases) %>%
  filter(grepl("Study", class)) %>%
  mutate(school = stringi::stri_extract(class, regex = "School \\d"),
         class = gsub("School \\d ", "", class))

```

## Assumptions

### Overview 

Infectious quanta from Buonanno 2020
* https://www.sciencedirect.com/science/article/pii/S0160412020320675?via%3Dihub
* Table 2 - Light activity, speaking
* Mean 6.98 x 10e-1; St.dev: 7.20 x 10e-1 quanta/hour

Number of infectious cases from this study
* take inferred infections
* assume that they are being infectious ~1-3 days before symptom onset
* https://link.springer.com/article/10.1007/s15010-020-01531-3
* https://academic.oup.com/cid/article/74/9/1678/6359063
* https://www.sciencedirect.com/science/article/pii/S1755436521000359
* --> use data by date of absence and shift cases to the left (with something half-normal shaped)
* for this, use infectiousness profile from He et al: https://www.nature.com/articles/s41591-020-0869-5#Sec1
* --> weight suspected cases accordingly


Time spent in school from this study
* use time spent in class room

Number of contacts from this study
* could possibly assume that they get in contact with all class mates

Rebreathed air fraction
* calculated from this study


### Infectiousness

```{r}
# Infectious profile
# shape, scale, start
inf_par <- c(20.51, 1.59, 12.27)

# plot
plot(NA, axes=F, ann=F, ylim=c(0,0.3), xlim=c(-10,8))
axis(2, las=1, at=0:3*0.1, lab=paste0(0:3*10,'%'))
abline(v=0, col=gray(0.8))
curve(dgamma(x+inf_par[3], inf_par[1], inf_par[2]), from=-10, to=8, add=T)
axis(1, at=(-5:4)*2, lab=(-5:4)*2, cex.axis=1)
mtext('Density', 2, line=3)
mtext('Days after symptom onset', 1, line=2.5)

# corresponding probability distribution
plot(dgamma(-10:0+inf_par[3], inf_par[1], inf_par[2]))

p_if <- function(x) {
  pgamma(x+.5+inf_par[3], inf_par[1], inf_par[2]) - pgamma(x-0.5+inf_par[3], inf_par[1], inf_par[2])
}

plot(sapply(-10:0, p_if))
```

## Estimation

### rebreathed air fraction

```{r}
palas_daily %>%
  ggplot(aes(x = date, y = f, color = intervention)) +
  facet_wrap(~ class) +
  geom_point()

palas_int %>%
  ggplot(aes(x = intervention, y = median_f)) +
  geom_point() +
  geom_errorbar(aes(ymin = median_f - sd_f, ymax = median_f + sd_f)) +
  facet_wrap(~ class)
```

### No. of infectious

```{r}
max_delay <- 7
p_if_week <- p_if(-max_delay:-1)

df_inf <- data.frame()

for (sc in study_classes) {
  
  redcap_sim_sc <- redcap_sim %>% 
    filter(class == sc) 
  
  for (ds in 1:max(redcap_sim_sc$dataset)) {
    
    redcap_sim_sc_ds <- redcap_sim_sc %>%
      filter(dataset == ds) %>%
      arrange(day)
    
    for (t in 1:(max(redcap_sim_sc_ds$day)-max_delay-1)) {
      
      start <- t+1
      end <- pmin((t+8), max(redcap_sim_sc_ds$day))
      
      n_inf <- sum(redcap_sim_sc_ds$new_cases[start:end],  rev(p_if_week))
      
      new_entry <- data.frame(
        school = redcap_sim_sc$school[1], 
        class = sc,
        dataset = ds,
        day = t,
        infectious = n_inf)
      
      df_inf <- rbind(df_inf, new_entry)
    }
  }
}

df_inf <- df_inf %>%
  left_join(redcap %>%
              select(school, class, day, date, intervention))

df_inf %>%
  select(-school) %>%
  ggplot(aes(x = day, y = infectious)) +
  facet_wrap(~ class) +
  stat_lineribbon(.width = .95) +
  scale_fill_manual(values = RColorBrewer::brewer.pal(9, "Blues")[4])

df_inf %>%
  group_by(school, class, day, intervention) %>%
  summarize(infectious = mean(infectious)) %>%
  ungroup() %>%
  group_by(school, class, intervention) %>%
  summarize(infectious = mean(infectious)) %>%
  ungroup() %>%
  ggplot(aes(x = intervention, y = infectious)) +
  geom_bar(stat = "identity")
```

### P transmission

```{r}
set.seed(12345)
draws <- 1e3


df_trisk <- df_inf %>%
  left_join(palas_daily %>% select(-day)) %>%
  filter(!is.na(weekday)) %>%
  rename(I = infectious) %>%
  mutate(n = n_room - 1) 

df_trisk_by_t <- data.frame() 
durations <- 45 * c(4, 6, 8, 10)
for (t in durations) {
  new_entry <- df_trisk %>%
    rowwise() %>%
    mutate(P = list(1 - exp(-f * I * rlnorm(draws, .698, .72) * t / n)),
           draws = list(1:draws)) %>%
    unnest() %>%
    mutate(school_h = t / 45)
  df_trisk_by_t <- rbind(df_trisk_by_t, new_entry)
}

df_trisk_by_t <- df_trisk_by_t %>% 
  mutate(class = paste(school, class),
         class = factor(class, levels = (c("School 1 Study (A)", "School 1 Study (B)", "School 2 Study"))),
         intervention = factor(intervention, levels = c("None", "Mask mandate", "Air filter"))) 

df_trisk_sum <- df_trisk_by_t %>%
  group_by(school, class, dataset, draws, intervention, school_h) %>%
  summarise(P = mean(P)) %>%
  ungroup()

df_trisk_sum_mean <- df_trisk_sum %>%
  group_by(intervention, school_h) %>%
  summarise(P = mean(P)) %>%
  ungroup() %>%
  mutate(school_h = ifelse(intervention == "None", school_h - .25, 
                           ifelse(intervention == "Air filter", school_h + .25, school_h)))

df_trisk_sum_mean_bySchool <- df_trisk_sum %>%
  group_by(school, intervention, school_h) %>%
  summarise(P = mean(P)) %>%
  ungroup() %>%
  mutate(school_h = ifelse(intervention == "None", school_h - .5, 
                           ifelse(intervention == "Air filter", school_h + .5, school_h)))


df_trisk_pl <- df_trisk_sum %>%
  ggplot(aes(x = school_h, y = P, color = intervention)) +
  geom_line(data = df_trisk_sum_mean) +
  stat_pointinterval(point_interval = "mean_qi", position = position_dodge(width = .5), fill = "white", shape = 21, .width = c(.5, .8, .95)) +
  scale_color_manual(values = c("black", cbPalette[1:2])) +
  scale_y_continuous(limits = c(0, 1), expand = c(0,0), labels = function(x) x * 100) +
  scale_x_continuous(breaks = durations / 45) +
  labs(color = "Intervention", y = "Estimated average daily probability of transmission (%)", x = "Duration of exposure (school-hours in 45min)") +
  theme_bw2() +
  theme(legend.position = "bottom", panel.spacing = unit(1, "lines"),
        plot.margin = unit(c(5.5, 7.5, 5.5, 5.5), "points"))

df_trisk_pl

save_plot(df_trisk_pl, pdf_file = "../results/results-transmission-risk.pdf", w = 12, h = 10)
  
df_trisk_bySchool_pl <- df_trisk_sum %>%
  ggplot(aes(x = school_h, y = P, color = intervention)) +
  facet_wrap(~ school, nrow = 1) +
  geom_line(data = df_trisk_sum_mean_bySchool) +
  stat_pointinterval(point_interval = "mean_qi", position = position_dodge(width = 1), fill = "white", shape = 21, .width = c(.5, .8, .95)) +
  scale_color_manual(values = c("black", cbPalette[1:2])) +
  scale_y_continuous(limits = c(0, 1), expand = c(0,0), labels = function(x) x * 100) +
  scale_x_continuous(breaks = durations / 45) +
  labs(color = "Intervention", y = "Estimated average daily probability of transmission (%)", x = "Duration of exposure (school-hours in 45min)") +
  theme_bw2() +
  theme(legend.position = "bottom", panel.spacing = unit(1, "lines"),
        plot.margin = unit(c(5.5, 7.5, 5.5, 5.5), "points"))

df_trisk_bySchool_pl

save_plot(df_trisk_bySchool_pl, pdf_file = "../results/supp-results-transmission-risk.pdf", w = 16, h = 10)
```
