---
title: "Transmission Risk"
author: "NB"
date: "2022-10-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(tidyverse)
library(tidybayes)
library(LaplacesDemon)
library(psych)
library(rstanarm)

source("../utils/plotting.R")
source("../utils/tex.R")
source("../helper/settings.r")
```

## Data

```{r}
# environmental data
palas <- read_csv("../data-clean/palas.csv") %>%
  mutate(weekday = factor(weekday, levels = paste0(c("Mon", "Tues", "Wednes", "Thurs", "Fri"), "day")),
         intervention = factor(intervention, levels = c("Mask mandate", "No intervention", "Air cleaner")))

# case data range  
redcap_full <- readRDS("../data-clean/redcap-full-range.rds")

redcap_sim <- meta_dat <- data.frame(folders = list.files("../fitted-models/multiverse", full.names = T),
                                     dataset = as.numeric(list.files("../fitted-models/multiverse"))) %>%
  mutate(sample_file = sapply(folders, list.files, pattern = "sample.rds", full.names = T)) %>%
  mutate(observed_data = lapply(sample_file, readRDS)) %>%
  unnest() %>%
  filter(school_class %in% c("School 1 (A)", "School 1 (B)", "School 2 (D)")) 
```

## Input

### Rebr. air fraction (f)

Use median rebreathed air fraction from this study

```{r}
rebAirFrac <- palas %>%
  group_by(school, date, intervention) %>%
  summarize(f = mean(f, na.rm = T)) %>% 
  ungroup() 
```

```{r}
rebAirFrac_pl <- rebAirFrac %>%
  ggplot(aes(x = school, color = intervention, y = f)) +
  geom_boxplot() +
  scale_color_manual(values = intervention_col) +
  labs(y = "Average rebreathed air fraction", title = "a") +
  theme_bw2() +
  theme(legend.position = "none", axis.title.x = element_blank())

rebAirFrac_pl
```


### No. of infectious (I)

Number of infectious cases from this study
* --> use data from probabilistic simulation and shift cases to the left (with something half-normal shaped)
* for this, use infectiousness profile from He et al: https://www.nature.com/articles/s41591-020-0869-5#Sec1
* take into account that some students stayed in school with symptoms (date absence - date symptoms)

```{r}
# Infectious profile
# shape, scale, start
inf_par <- c(20.51, 1.59, 12.27)

# plot
plot(NA, axes=F, ann=F, ylim=c(0,0.3), xlim=c(-10,8))
axis(2, las=1, at=0:3*0.1, lab=paste0(0:3*10,'%'))
abline(v=0, col=gray(0.8))
curve(dgamma(x+inf_par[3], inf_par[1], inf_par[2]), from=-10, to=8, add=T)
axis(1, at=(-5:4)*2, lab=(-5:4)*2, cex.axis=1)
mtext('Density', 2, line=3)
mtext('Days after symptom onset', 1, line=2.5)

# corresponding probability distribution
inf_dens_pl <- data.frame(x = -7:3) %>%
  mutate(y = dgamma(x+inf_par[3], inf_par[1], inf_par[2])) %>%
  ggplot(aes(x = x, y = y)) +
  geom_line() +
  geom_vline(aes(xintercept = 0), linetype = "dotted", alpha = .5) +
  labs(x = "Days since symptom onset", y = "Density") +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  theme_bw2()

inf_dens_pl

# compute infectiousness, i.e. relative probability of transmission
p_if <- function(x) {
  max_dens <- max(dgamma(seq(-5, 5, 1)+inf_par[3], inf_par[1], inf_par[2]))
  dgamma(x+inf_par[3], inf_par[1], inf_par[2]) / max_dens
}


inf_prob_pl <- data.frame(x = -7:3) %>%
  mutate(y = p_if(x)) %>%
  ggplot(aes(x = x, y = y)) +
  geom_line() +
  geom_vline(aes(xintercept = 0), linetype = "dotted", alpha = .5) +
  labs(x = "Days since symptom onset", y = "Relative prob. of transmission (%)", title = "a") +
  scale_x_continuous(expand = c(0,0), breaks = seq(-10, 4, 2)) +
  scale_y_continuous(expand = c(0,0), labels = function(x) x * 100) +
  theme_bw2()

inf_prob_pl
```

```{r}
study_period <- seq(min(redcap_full$date), max(redcap_full$date), by = "1 day")

infectious <- data.frame()

for (sc in c("School 1 (A)", "School 1 (B)", "School 2 (D)")) {
  
  redcap_sim_sc <- redcap_sim %>% 
    filter(school_class == sc) 
    
    message(sprintf("Class: %s", sc))
  
  for (ds in 1:max(redcap_sim_sc$dataset)) {
    
    redcap_sim_sc_ds <- redcap_sim_sc %>%
      filter(dataset == ds) %>% 
      arrange(date_start)
    
    for (t in seq_along(study_period)) {
      
      redcap_sim_sc_ds <- redcap_sim_sc_ds %>%
        filter(date_start > study_period[t]) %>%
        mutate(days_since_symptoms = as.numeric(study_period[t]-date_symptoms),
               prob_infectious = p_if(days_since_symptoms))
      
      new_entry <- data.frame(
        school = redcap_sim_sc$school[1], 
        class = redcap_sim_sc$class[1],
        school_class = sc,
        dataset = ds,
        date = study_period[t],
        I = sum(redcap_sim_sc_ds$prob_infectious))
      
      infectious <- rbind(infectious, new_entry)
    }
  }
}
```

```{r}
infectious %>%
  group_by(school_class, date) %>%
  summarise(I = mean(I)) %>%
  ungroup() %>%
  ggplot(aes(x = date, y =  I)) +
  geom_step() +
  facet_wrap(~ school_class)
```

```{r}
infectious_sub <- infectious %>%
  left_join(redcap_full) %>%
  # remove the last study week, the week before vacation, and the vacation weeks
  mutate(study_week = week - 3) %>%
  filter(study_week > 0,
         ifelse(school == "School 1" & study_week %in% c(2,3,4,9), F, T),
         ifelse(school == "School 2" & study_week %in% c(2,3,8,9), F, T)) %>%
  filter(!(weekday %in% c("Saturday", "Sunday"))) %>%
  group_by(school, class, date, intervention) %>%
  summarise(I = mean(I)) %>%
  ungroup() 
```

```{r}
infectious_sub_pl <- infectious_sub %>%
  ggplot(aes(x = class, color = intervention, y = I)) +
  geom_boxplot() +
  scale_color_manual(values = intervention_col) +
  labs(y = "Estimated average number\nof infectious students", title = "b") +
  theme_bw2() +
  theme(legend.position = "none", axis.title.x = element_blank(), legend.title = element_blank())

infectious_sub_pl
```

### No. of contacts (n)

Use the number of students in the class from this study

```{r}
ncontacts <- redcap_full %>%
  filter(class %in% c("A", "B", "D")) %>%
  group_by(school, class, date, intervention) %>%
  slice(1) %>%
  mutate(n = (n_class - n_absent) + 1) %>% # +1 teacher
  ungroup() %>%
  select(school, class, date, intervention, n)
```

```{r}
ncontacts_pl <- ncontacts %>%
  ggplot(aes(x = class, color = intervention, y = n)) +
  geom_boxplot() +
  scale_color_manual(values = intervention_col) +
  labs(y = "Number of students in class", title = "c") +
  theme_bw2() +
  theme(legend.position = "right", axis.title.x = element_blank(), legend.title = element_blank())

ncontacts_pl
```

### Infectious quanta (q)

Infectious quanta from Buonanno 2020
* https://www.sciencedirect.com/science/article/pii/S0160412020320675?via%3Dihub
* Table 2:
* - Light activity, speaking (log10 ERq): Mean 6.98 x 10e-1; St.dev: 7.20 x 10e-1 quanta/hour
* - Breathing: 4.29 x 10e-1
* - Singing: 1.50 x 10e0

```{r}
m_q = 6.98
s_q = 7.2
logs_q = sqrt(log(s_q ^ 2 / m_q ^ 2 + 1))
logm_q = log(m_q) - logs_q ^ 2 / 2

inf_quanta_pl <- data.frame(x = seq(0, 25, .1)) %>%
  mutate(y = dlnorm(x, logm_q, logs_q)) %>%
  ggplot(aes(x = x, y = y)) +
  geom_line() +
  geom_vline(aes(xintercept = 0), linetype = "dotted", alpha = .5) +
  labs(x = "Infectious quanta (p/h)", y = "Density") +
  scale_x_continuous(expand = c(0,0), breaks = seq(0, 25, 5)) +
  scale_y_continuous(expand = c(0,0)) +
  theme_bw2()

inf_quanta_pl
```

```{r}
rq <- function(q) qlnorm(q, logm_q, logs_q)
quantas <- c(4.29, 6.98, 15.00)
quanta_names <- paste0(c("Breathing (", "Speaking (", "Singing ("), round_k(quantas, 2), " quanta/h)")
```

### Exposure time (t)

Estimate transmission risk for 6 hours school day.

```{r}
exposure_t <- 6
```


## Modeling Risk

```{r}
# rebreathed air fraction
f_mean <- mean(rebAirFrac$f)
message(sprintf("Average rebreathed air fraction: %f percent", round(100 * f_mean, 1)))

# share of infectious people
In <- left_join(ncontacts, infectious_sub) %>%
  mutate(In = I / n) 
In_mean <- mean(In$In, na.rm = T)
message(sprintf("Average share of infectious people: %f percent", round(100 * In_mean, 1)))

# infectious quanta 
q_red <- data.frame(
  estimate = c("mean", "lower", "upper"),
  masks = c(0.69, 0.41, 0.86),
  aircleaner = c(0.39, 0.04, 0.68)
)

# taken together
transRisk <- data.frame(f = f_mean,
                         In = In_mean,
                         t = exposure_t,
                         activity = quanta_names,
                         standard = quantas) %>%
  crossing(q_red) %>%
  mutate(masks = (1-masks) * standard,
         aircleaner = (1-aircleaner) * standard,
         standard = standard) %>%
  melt(c("f", "In", "t", "estimate", "activity")) %>%
  rename(intervention = variable,
         q = value) %>%
  mutate(intervention = ifelse(grepl("masks", intervention), "Mask mandate", 
                               ifelse(grepl("aircleaner", intervention), "Air cleaner", "No intervention")),
         P = 100 * (1 - exp(- f * In * t * q))) %>%
  select(activity, estimate, intervention, P) %>%
  dcast(intervention + activity ~ estimate) %>%
  mutate(activity = factor(activity, levels = quanta_names),
         intervention = factor(intervention, levels = c("No intervention", "Mask mandate", "Air cleaner")))

# Plot
transRisk_pl <- ggplot(mapping = aes(x = intervention)) +
  facet_wrap(~ activity) +
  geom_errorbar(data = transRisk %>% filter(intervention != "No intervention"), aes(ymin = lower, ymax = upper, color = intervention),
                size = 1, width = .1) +
  geom_point(data = transRisk %>% filter(intervention != "No intervention"), aes(y = mean, color = intervention),
             size = 2, fill = "white") +
  geom_hline(data = transRisk %>% filter(intervention == "No intervention"), aes(yintercept = mean),
             linetype = "dashed") +
  geom_text(data = transRisk %>% filter(intervention == "No intervention"), aes(label = "No intervention", y = mean + .5, 1),
            size = 8 / cm(1)) +
  scale_color_manual(values = cbPalette[1:2]) +
  labs(y = "Risk of infection (%)") +
  theme_bw2() +
  theme(legend.position = "top", legend.title = element_blank(),
        axis.title.x = element_blank())

transRisk_pl
save_plot(transRisk_pl, "../results/results-transmission-risk.pdf", w = 16, h = 7)

# Numbers
transRisk %>%
  mutate_if(is.numeric, round_k, 1) %>%
  select(intervention, activity, mean, upper, lower) %>%
  filter(activity == "Speaking (6.98 quanta/h)") %>%
  mutate(intervention = factor(intervention, levels = c("Mask mandate", "Air cleaner", "No intervention"))) %>%
  arrange(intervention)
```
